|

### 2019-07-16 inst/manuscript/manuscript.Rmd
Update Figure 5

# plot heatmap
f5_htmp <- plot_heatmap(mt = f5_table_filt, 
                        plot = TRUE,
                        df = FALSE, 
                        data_type = "log2fc", 
                        clust_fun = "gower", 
                        split_type = "cutree", 
                        k = 7, 
                        cluster_split = FALSE, 
                        split_order = c(4, 1, 6, 2, 3, 5, 7), 
                        colour_lims = c(-4, 4),
                        column_labels = c("ATCC90028", "ATCC10231", 
                                          "DAY286 Y", "DAY286 B"), 
                        col_name_fontsize = 6, 
                        column_names_rot = 45, 
                        row_title = c("1", "2", "3", "4", "5", "6", "7"), 
                        row_title_fontsize = 6, 
                        row_title_rot = 0, 
                        heatmap_legend_param = f5_params)

@@

# extract identifiers from each cluster
f5_clust1 <- f5_clusters %>% 
  filter(cluster == 1) %>% 
  mutate(id = gsub("PEP1", "CaO19.3767", id)) %>% 
  pull(id) %>% 
  stringr::str_extract_all(., "[^;]+") %>% 
  unlist()

f5_clust2 <- f5_clusters %>% 
  filter(cluster == 2) %>% 
  pull(id)

@@

# cluster 5 has too many proteins to fit in table
# but GO enrichment still possible
f5_clust5 <- f5_clusters %>% 
  filter(cluster == 5) %>% 
  mutate(id = gsub("ALA1", "CaO19.5746", id), 
         id = gsub("MDH1", "CaO19.7481", id), 
         id = gsub("RPS1", "CaO19.3002", id), 
         id = gsub("TSA1", "CaO19.7417", id)) %>% 
  pull(id) %>% 
  stringr::str_extract_all(., "[^;]+") %>% 
  unlist() %>% 
  unique()

# cluster 6 is proteins that could not be clustered
# because all 4 log2FCs = NA
f5_clust6 <- sort(rownames(f5_table_excl))

# import FungiFun2 results
f5_go1 <- process_fungifun("figures/f5_GO_clust1.csv") %>% 
  mutate(Prot.found = gsub("CaO19.3767", "PEP1", Prot.found))

# issue with PEP1, ambiguous ID in FungiFun, used CaO19.3767 as identifier
f5_go2 <- process_fungifun("figures/f5_GO_clust2.csv")

@@

# issue with ALA1, MDH1, used CaO19.5746 and CaO19.7481 as identifiers
f5_go5 <- process_fungifun("figures/f5_GO_clust5.csv") %>% 
  mutate(Prot.found = gsub("CaO19.5746", "ALA1", Prot.found), 
         Prot.found = gsub("CaO19.7481", "MDH1", Prot.found), 
         Prot.found = gsub("CaO19.3002", "RPS1", Prot.found), 
         Prot.found = gsub("CaO19.7417", "TSA1", Prot.found))

f5_go6 <- process_fungifun("figures/f5_GO_clust6.csv")
```

@@

f5_cap <- "\\textbf{Identification of commonly enriched EV proteins across 
           different \\textit{C. albicans} strains.} Heatmap of proteins 
           (n = 396) identified in all four EV samples (venn overlap in Figure 
           \\@ref(fig:figure4)A). Each column represents a 
           \\textit{C. albicans} strain and each row represents a protein. The 
           colours indicate the log\\textsubscript{2}(FC) of the protein for 
           that particular strain; red is EV enriched, blue is EV depleted, and 
           black is EV exclusive. Unsupervised clustering of rows and columns 
           was performed using Gower's formula via the daisy function from the 
           R package \\textit{cluster} [@maechler2019]. Proteins which were 
           exclusive to EVs from all four strains could not be clustered and 
           were seperated prior to clustering, in the group designated 
           \`\`cluster 6\". Functional enrichment analyses were performed on 
           the heatmap protein clusters using the online tool FungiFun2 
           [@priebe2015]. A selection of significantly enriched GO terms are 
           presented in the table inset. Lists of the proteins identified in 
           each cluster are shown and are also available in supplemental 
           File S5. \\textsuperscript{a} indicates where all proteins from 
           each protein group in the cluster were used for the GO analysis."
```

>>>>

# plot heatmap
f5_htmp <- plot_heatmap(mt = f5_table_filt, 
                        plot = FALSE,
                        df = FALSE, 
                        data_type = "log2fc", 
                        clust_fun = "gower", 
                        split_type = "cutree", 
                        k = 7, 
                        cluster_split = FALSE, 
                        split_order = c(4, 1, 6, 2, 3, 5, 7), 
                        colour_lims = c(-4, 4),
                        column_labels = c("ATCC90028", "ATCC10231", 
                                          "DAY286 Y", "DAY286 B"), 
                        col_name_fontsize = 6, 
                        column_names_rot = 45, 
                        row_title = c("1", "2", "3", "4", "5", "6", "7"), 
                        row_title_fontsize = 6, 
                        row_title_rot = 0, 
                        heatmap_legend_param = f5_params)

@@

# extract identifiers from each cluster
f5_clust1_2 <- f5_clusters %>% 
  filter(cluster == 1 | cluster == 2) %>% 
  mutate(id = gsub("PEP1", "CaO19.3767", id)) %>% 
  pull(id) %>% 
  stringr::str_extract_all(., "[^;]+") %>% 
  unlist()

@@

# cluster 5 has too many proteins to fit in table
# but GO enrichment still possible
f5_clust5 <- f5_clusters %>% 
  filter(cluster == 5) %>% 
  mutate(id = gsub("RPS1", "CaO19.3002", id)) %>% 
  pull(id) %>% 
  stringr::str_extract_all(., "[^;]+") %>% 
  unlist() %>% 
  unique()

f5_clust6 <- f5_clusters %>% 
  filter(cluster == 6) %>% 
  mutate(id = gsub("ALA1", "CaO19.5746", id), 
         id = gsub("MDH1", "CaO19.7481", id), 
         id = gsub("TSA1", "CaO19.7417", id)) %>% 
  pull(id) %>% 
  stringr::str_extract_all(., "[^;]+") %>% 
  unlist() %>% 
  unique()

f5_clust7 <- f5_clusters %>% 
  filter(cluster == 7) %>% 
  pull(id)

# cluster 6 is proteins that could not be clustered
# because all 4 log2FCs = NA
f5_clust8 <- sort(rownames(f5_table_excl))

# import FungiFun2 results
# issue with PEP1, ambiguous ID in FungiFun, used CaO19.3767 as identifier
f5_go1_2 <- process_fungifun("figures/f5_GO_clust1_2.csv") %>% 
  mutate(Prot.found = gsub("CaO19.3767", "PEP1", Prot.found))

@@

# issue with ALA1, MDH1, used CaO19.5746 and CaO19.7481 as identifiers
f5_go5 <- process_fungifun("figures/f5_GO_clust5.csv") %>% 
  mutate(Prot.found = gsub("CaO19.3002", "RPS1", Prot.found))

f5_go6 <- process_fungifun("figures/f5_GO_clust6.csv") %>% 
  mutate(Prot.found = gsub("CaO19.5746", "ALA1", Prot.found), 
         Prot.found = gsub("CaO19.7481", "MDH1", Prot.found), 
         Prot.found = gsub("CaO19.7417", "TSA1", Prot.found))

f5_go7 <- process_fungifun("figures/f5_GO_clust7.csv")

f5_go8 <- process_fungifun("figures/f5_GO_clust8.csv")
```

@@

f5_cap <- "\\textbf{Identification of commonly enriched EV proteins across 
           different \\textit{C. albicans} strains.} Heatmap of proteins 
           (n = 396) identified in all four EV samples (venn overlap in Figure 
           \\@ref(fig:figure4)A). Each column represents a 
           \\textit{C. albicans} strain and each row represents a protein. The 
           colours indicate the log\\textsubscript{2}(FC) of the protein for 
           that particular strain; red is EV enriched, blue is EV depleted, and 
           black is EV exclusive. Unsupervised clustering of rows and columns 
           was performed using Gower's formula via the daisy function from the 
           R package \\textit{cluster} [@maechler2019]. Proteins which were 
           exclusive to EVs from all four strains and therefore had no valid 
           log\\textsubscript{2}(FC) values
           were seperated prior to clustering, in the group designated 
           \`\`cluster 8\". Functional enrichment analyses were performed on 
           the heatmap protein clusters using the online tool FungiFun2 
           [@priebe2015]. A selection of significantly enriched GO terms are 
           presented in the table inset. Full lists of enriched GO terms are 
           available in supplemental File S3. Full lists of the proteins 
           in each cluster are available in supplemental File S5.
```
